Tabular Constraint Learning

### 2016-04-01 Paper/ECAI/tabular.tex
added short related work annotation
text

\begin{abstract}
  abstract
  \end{abstract}
\section{Introduction}
\sergey{we need structure} test

\section{Related Work}
\sergey{ECAI reference style file ignores their guideline and their guideline ignores what is written in the guidelines!}
flashfill, flashextract, flashmeta \cite{flashfill,flashextract,flashmeta}
\begin{itemize}
  \item their supervised vs our unsupervised approach
  \item they look for a single ``smallest'' solution, we enumerate them all
  \item they are looking for a function, we solve constraint satisfaction problems
  \item we do not assume classic row based data layout, we work in the tabular setting
\end{itemize}

@@

\begin{itemize}
  \item not designed for excel-like data representation (type consistency, groups, etc)
  \item not designed for excel-like constraints (lookups, conditional ifs, etc)
  \item does not support user extensions (?)
\end{itemize

>>>>

\begin{abstract}
  abstract
  \end{abstract}
\section{Introduction}
\sergey{bullet points for luc to start introduction}\\
\textbf{Key question}:\\
Can we discover or reconstruct structural relations in flat tabular spreadsheet data? [in a general way that allows declarative specification of constraints to discover]\

\textbf{Motivation}:
\begin{itemize}
  \item File generated from model, model got lost - > reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

\textbf{Novelty:}
\begin{itemize}
  \item Unsupervised setting (contrary to flashfill, etc)
  \item Numeric, different constraints (contrary to single textual function solution in flashfill, etc)
  \item Data format (2D) -- data is no longer in rows like a classic ML or DM settings
  \item Declarative, general / modular, stacking of constraint problems 
\end{itemize}

\sergey{we need structure here}

\textbf{Approach}
\begin{itemize}
  \item Notation
  \item Algorithm (select constraints, find assignments, find solutions)
\end{itemize}

{\bfseries 
  Experimental questions
}
\begin{itemize}
  \item  How accurate are we? (Accuracy / recall)
  \item  How fast are we and which factors affect the runtime (how)?
  \item  How general is our approach, what limitations are there?
\end{itemize}

\section{Related Work}
\sergey{key bullet points for Luc and possibly Samuel and me to make related work section}

\sergey{ECAI reference style file ignores their guideline and their guideline ignores what is written in the guidelines!}
flashfill, flashextract, flashmeta \cite{flashfill,flashextract,flashmeta}
\begin{itemize}
  \item their supervised vs our unsupervised approach
  \item they look for a single ``smallest'' solution, we enumerate them all
  \item they are looking for a function, we solve constraint satisfaction problems
  \item we do not assume classic row based data layout, we work in the tabular setting
\end{itemize}

@@

\begin{itemize}
  \item not designed for excel-like data representation (type consistency, groups, etc)
  \item not designed for excel-like constraints (lookups, conditional ifs, etc)
  \item does not support user extensions (?)
\end{itemize}
